The Effects of Stellar Binarity on Transit Survey Occurrence Rates

### 2017-10-05 paper/ms.tex
wordsmith
corrected f_d2c bug

However, the distance out to which double stars are {\it selected} is 
different from the distance $d_{{\rm max},d}^{\rm p}$ out to which planets can 
be {\it detected} (around the primary of a double star system).
For a population with fixed  $\gamma_R$, since ${\rm S/N} \propto \mathcal{D} 
L^{1/2} d^{-1}$,
\begin{equation}
d_{{\rm max},d}^{\rm p} = (1 + \gamma_R)^{-1/2} d_{{\rm max},s} = 
(1 + \gamma_R)^{-1} d_{{\rm max},d}.
\end{equation}
For $\gamma_R = 1$, this means only 1 in 8 apparently-searchable stars which 
are in fact binary systems can yield detectable planets (the ratio of 
volume in which planets can be detected to the actual selected volume).
For a more realistic sample, $\gamma_R \approx 0.1$, and there is an 
interesting asymmetry.
One finds the completeness for planets which orbit the primary star, 
$f_{d1,c}$ to be
\begin{equation}
f_{d1,c} = (1+\gamma_R)^{-3} \approx 3/4.
\end{equation}
However, for planets which orbit the secondary star, the completeness is
\begin{equation}
f_{d2,c} = (1+\gamma_R^{-1})^{-3} \approx 3/4000.
\end{equation}

@@

For planets detected in binary systems,
\begin{equation}
N_{{\rm det},d}
= 
N_d \Gamma_{t,d} (f_{d1,g}f_{d1,c} + f_{\rm desired}w_{d2}f_{d2,g}f_{d2,c}).
\label{eq:N_det_d_model2}
\end{equation}
The factor $f_{\rm desired}$, as previously discussed, accounts for the 
fraction of secondaries not of the desired {\it stellar} type. The above 
counts the total number of detected planets around stars of the desired type, 
though all these planets have diluted radii.
The detection and geometric transit probabilities for a given system are
\begin{align}
f_{d1,c} &= (1+\gamma_R)^{-3} \\
f_{d1,g} &= f_{s,g} \\
f_{d2,c} &= (1+\gamma_R^{-1})^{-3} \\
f_{d2,g} &= f_{s,g}q^{2/3}.
\end{align}

@@

Keep the same stars as in Sec.~\ref{sec:model_2}.
Now let the planets have a power-law radius distribution, ${\rm d}N_p/{\rm 
d}R_p\propto R_p^\delta$. 
We want to know the effects of binarity on the apparent distribution of 
planetary radii.
Specifically, the average number of planets in a given size range per star of 
the desired type in this universe is
\begin{equation}
\frac{N_{\rm planets}(R_p^{\rm min}<R_p <R_p^{\rm max})}{N_{\rm stars}} = 
\Gamma_0 \int_{R_p^{\rm min}}^{R_p^{\rm max}} R_p^\delta \,{\rm d}R_p,
\end{equation}
for $\Gamma_0$ one of $\{\Gamma_{t,s}, \Gamma_{t,d}, w_{d2}\Gamma_{t,d}\}$
corresponding to single star systems, the primaries of double star systems, 
and the secondaries of double star systems.

>>>>

However, the distance out to which double stars are {\it selected} is 
different from the distance $d_{{\rm max},d}^{\rm p}$ out to which planets can 
be {\it detected} (around the primary of a double star system).
For the binary twin population, since ${\rm S/N} \propto \mathcal{D} 
L^{1/2} d^{-1}$,
\begin{equation}
d_{{\rm max},d}^{\rm p} = (1 + \gamma_R)^{-1/2} d_{{\rm max},s} = 
(1 + \gamma_R)^{-1} d_{{\rm max},d}.
\end{equation}
For $\gamma_R = 1$, this means only 1 in 8 apparently-searchable stars which 
are in fact binary systems can yield detectable planets (the ratio of 
volume in which planets can be detected to the actual selected volume).

@@

For planets detected in binary systems,
\begin{equation}
N_{{\rm det},d}
= 
N_d \Gamma_{t,d} (f_{d1,g}f_{d1,c} + f_{\rm desired}w_{d2}f_{d2,g}f_{d2,c}).
\label{eq:N_det_d_model2}
\end{equation}
The factor $f_{\rm desired}$, as previously discussed, accounts for the 
fraction of secondaries not of the desired {\it stellar} type. The above 
counts the total number of detected planets around stars of the desired type, 
though all these planets have diluted radii.
The detection and geometric transit probabilities for a given system are
\begin{align}
f_{d1,c} &= (1+\gamma_R)^{-3} \\
f_{d1,g} &= f_{s,g} \\
f_{d2,c} &= (1+\gamma_R^{-1})^{-3} \gamma_R^{-6/\alpha} 
\label{eq:f_d2c}\\
f_{d2,g} &= f_{s,g}q^{2/3},
\end{align}
where typically $\alpha=3.5$ (and the second term in Eq.~\ref{eq:f_d2c} comes 
from the stellar radius correction).
For a typical binary drawn from the local stellar neighborhood, $\gamma_R 
\approx 0.2$ (see Fig.~\ref{fig:gammaR_distribn_mag_limited}), and there is an 
interesting asymmetry.
One finds the completeness for planets which orbit the primary star, 
$f_{d1,c}$ to be
\begin{equation}
f_{d1,c} = (1+\gamma_R)^{-3} \sim 70\%
\end{equation}
However, for planets which orbit the secondary star, the completeness is
\begin{equation}
f_{d2,c} = (1+\gamma_R^{-1})^{-3} \gamma_R^{-6/\alpha} \sim 7\%.
\end{equation}
Controlling for all other variables, in the typical binary system planets 
around secondaries are more difficult to detect than those around primaries.

@@

Keep the same stars as in Sec.~\ref{sec:model_2}.
Now let the planets have a power-law radius distribution, ${\rm 
d}(N_p/N_\star)/{\rm 
d}R_p\propto R_p^\delta$. 
We want to know the effects of binarity on the apparent distribution of 
planetary radii.
Specifically, the average number of planets in a given size range per star of 
the desired type in this universe is
\begin{equation}
\frac{N_{\rm p}(R_p^{\rm \ell}<R_p <R_p^{\rm u})}{N_{\rm \star}} = 
\Gamma_0 \int_{R_p^{\rm \ell}}^{R_p^{\rm u}} R_p^\delta \,{\rm d}R_p,
\end{equation}
for $\Gamma_0$ one of $\{\Gamma_{t,s}, \Gamma_{t,d}, w_{d2}\Gamma_{t,d}\}$
corresponding to single star systems, the primaries of double star systems, 
and the secondaries of double star systems.
